Applications of the Fresnel Integrals

### 2019-03-17 draft.tex
rewritten 3.2

\FloatBarrier 
\subsection{Railway  Construction}

An object traveling on a circular path experiences a centripetal acceleration. The same happens when a train that travels on a straight path suddenly transitions to a tangential circular path. This sudden centripetal acceleration causes much discomfort for the driver as well as the passengers on the train.

In order to provide a smooth riding experience, much effort has been made in the history of railway construction. According to \cite{Lev08}, Mr. Gravatt was the first one who designed a sine curve around the year of 1828. Later by 1842, William Froude proposed to use a curve approximating the elastic curve, for the purpose of making the change of curvature by degree. In the year of 1880, Charles Crandall gives priority for the ``true transition curve'' to Ellis Holbrook in the Railroad Gazette. However, Arthur Talbot was among the first to approach the problem mathematically as he describes the problem and his solution in the introduction to ``The Railway Transition Spiral'' \cite{Tal99}:

@@

Given the expression of centripetal acceleration $V^{2} / R$, the obvious solution is to provide an easement curve whose curvature, $1/R$, increases linearly with the traveled distance. This geometry is an Euler spiral.

Unaware of the solution of the geometry by Leonhard Euler, Rankine cited the cubic curve (a polynomial curve of degree 3), which is an approximation of the Euler spiral for small angular changes in the same way that a parabola is an approximation to a circular curve.

Marie Alfred Cornu (and later some civil engineers) also solved the calculus of Euler spirals independently. Euler spirals are now widely used in rail and highway engineering for providing a transition or an easement between a tangent and a horizontal circular curve.

>>>>

\FloatBarrier 
\subsection{Railway  Construction}
An object traveling at speed $v$ on a circular path of radius $R$ experiences a centripetal acceleration $a$ as
$$  a = v^2/R.
$$ When a vehicle that travels on a straight path suddenly transitions to a circular path, then the acceleration sensed by the passengers suddenly changes from $0$ for the straight segment ($1/R=0$) to some positive value ($a>0$, because $1/R>0$). This sudden centripetal acceleration gives much discomfort for the driver as well as the passengers on the vehicle.  The effect is small when, e.g.~the first trains traveled at quite low speeds, but becomes much stronger when the speed increases ($a\sim v^2$).  Therefore increased speeds of trains triggered the quest for better designed tracks.  According to \cite{Lev08}, Mr. Gravatt was the first one who choose a sine curve for the transition from a straight segment to a curve around the year of 1828. Later in 1842, William Froude proposed the use of an elastic curve in order to make the change of curvature more smooth. In 1880, Charles Crandall asks for priority for the ``true transition curve'' in the Railroad Gazette.  The problem is officially on to Ellis Holbrook to be solved, however, Arthur Talbot was among the first to approach the problem mathematically.  He describes the problem and his solution in the introduction to ``The Railway Transition Spiral'' \cite{Tal99} which we quote here for being pronounced:

@@

Given the centripetal acceleration $a=v^2/R$, an obvious solution is to construct a curve whose curvature, $\kappa=1/R$, increases linearly with the traveled distance. This is the geometry of an Euler spiral \eqref{e:eulerSpiral}.

Rankine did not know of the solution of the geometry problem by Leonhard Euler.  Instead he proposed a cubic curve (a polynomial degree 3, $z(x)=ax^3+bx^2+cx+d$ with some adaptable coefficients $a,b,c,d$), an approximation of the exact solution for small angular changes.   We can compare this to a parabola approximating a circle near a point.

Marie Alfred Cornu (and later other civil engineers) also solved the problem of Euler spirals independently. Euler spirals are now-a-days widely used in railroad and highway construction, because they provide a smooth transition, i.e.~an easement, between a straight horizontal and an inclined track connected by a circular curve.
